Learning Causally-Generated Stationary Time Series

### 2017-02-23 doc/paper.tex
Some updates

\usepackage[accepted]{icml2017}  % option: accepted
\icmltitlerunning{Learning Causally-Generated Stationary Time Series}

@@

Let the \textit{mean-field} (MF) approximation $q(f,u,z)=p(f\cond u, z)q(u)q(z)$ of $p(f,u,z\cond e)$ be such that it is closest to $p(f,u,z\cond e)$ in Kullback-Leibler divergence. Rearranging
\begin{align*}
    &\log p(e) - \KL(q(f,u,z)\|p(f,u,z\cond e)) \\
    &\quad= \ll\la \log \frac{p(e\cond f)\cancel{p(f\cond u, z)}p(u)p(z)}{\cancel{p(f\cond u, z)}q(u)q(z)} \rr\ra_{q(f,u,z)} \\
    &\quad= \underbrace{\la \log p(e\cond f) \ra_{q(f,u,z)}}_{\text{reconstruction cost}} \\
    &\quad\phan{=}- \underbrace{\ll(\ll\la\log\frac{q(u)}{p(u)}\rr\ra_{q(u)} + \ll\la\log\frac{q(z)}{p(z)}\rr\ra_{q(z)}\rr)}_{\text{divergence from prior}} \\
    &\quad=\mathcal{L}[q(u),q(z)]
\end{align*}
shows that we can find $q(u)$ and $q(z)$ through maximising $\mathcal{L}$. Since $\log p(e)\ge\mathcal{L}$, $\mathcal{L}$ is called the \textit{evidence lower bound} (ELBO). Observe that maximisation of $\mathcal{L}$ attempts to explain the data well whilst not diverging too far from the model prior.

@@

Variational mean-field (MF) approaches to inference, like the one just presented, are often computationally efficient, but they are known to suffer from certain biases \cite{MacKay:2002:Information_Theory_Learning,Turner:2011:Two_Problems_With_Variational_Expectation,Murphy:2012:Probabilistic_Perspective}. We therefore further refine the MF approximation to alleviate these biases.

@@

\subsection{RLC Series Circuit}
Consider the voltage response $f(t)$ of a series circuit consisting of a resistance $R$, capacitance $C$, and inductance $L$ excited by current $x(t)$ with unity PSD due to thermal noise of the resistance. Application of Kirchhoff's voltage law \cite{Irwin:2010:Basic_Engineering_Circuit_Analysis} yields that
\begin{align*}
     L f'(t) + R f(t)+\frac{1}{C}\int^t f(t)\id{t} = x(t).
\end{align*}
Assume that the circuit is critically damped and that $R=2$ and $L=1$. Then $f(t)$ is of the form of \cref{eq:model} where $h(t) = t \exp(-t)$. Therefore, according to \cref{mod:cgpcm2}, it holds that $f(t) \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ where
\begin{align*}
    k_{f\cond h}(r) = \frac{1}{4}(1+|r|)\exp(-|r|).
\end{align*}

@@

\subsection{Unvoiced Fricatives}
Unvoiced fricatives are consonants produced by forcing air through a narrow constriction in the vocal tract, thereby creating a noisy, turbulant sound \cite{Taylor:2009:Text-To-Speech_Synthesis}.

@@

@@

In future research on the CGPCM, various directions can be explored: First, the model could be extented to multidimensional input and output spaces by following a construction similar to that by \citet{Bruinsma:2016:GGPCM}. Second, the application of more efficient sparse approximation for $h$ and $x$, such as the tree-structured approximation \cite{Bui:2014:Tree-Structured_Gaussian}, would scale the CGPCM to larger data sets. Third, to deal with signals that are band-limited, but not necessarily baseband, the use of an harmonic interdomain transformation \cite{Tobar:2015:Inter-Domain_Inducing} could be explored. Fourth, in the low noise case, ESS has a hard time exploring $q(u)$; therefore, in that case, afternative sampling algorithms such as Hamiltonian Monte-Carlo \cite{Neal:2012:MCMC_Using_Hamiltonian_Dynamics} could be used. Finally, using an approach similar to that by \citet{Lazaro-Gredilla:2013:Variational_Inference_for_Mahalanobis_Distance}, Bayesian inference in the hyperparameters could be attempted.

>>>>

\usepackage{icml2017}  % option: accepted
\icmltitlerunning{Learning Causally-Generated Stationary Time Series}

@@

Specifically, let the \textit{mean-field} (MF) approximation $q(f,u,z)=p(f\cond u, z)q(u)q(z)$ of $p(f,u,z\cond e)$ be such that it is closest to $p(f,u,z\cond e)$ in Kullback-Leibler divergence. Rearranging
\begin{align*}
    &\log p(e) - \KL(q(f,u,z)\|p(f,u,z\cond e)) \\
    &\quad= \ll\la \log \frac{p(e\cond f)\cancel{p(f\cond u, z)}p(u)p(z)}{\cancel{p(f\cond u, z)}q(u)q(z)} \rr\ra_{q(f,u,z)} \\
    &\quad= \underbrace{\la \log p(e\cond f) \ra_{q(f,u,z)}}_{\text{reconstruction cost}} \\
    &\quad\phan{=}- \underbrace{\ll(\ll\la\log\frac{q(u)}{p(u)}\rr\ra_{q(u)} + \ll\la\log\frac{q(z)}{p(z)}\rr\ra_{q(z)}\rr)}_{\text{divergence from prior}} \\
    &\quad=\mathcal{L}[q(u),q(z)]
\end{align*}
shows that we can find $q(u)$ and $q(z)$ through maximising $\mathcal{L}$. Since $\log p(e)\ge\mathcal{L}$, $\mathcal{L}$ is called the \textit{evidence lower bound} (ELBO). Observe that maximisation of $\mathcal{L}$ attempts to explain the data well whilst not diverging too far from the model prior.

@@

Variational mean-field (MF) approaches to inference, like the one just presented, are often computationally efficient, but they are known to suffer from certain biases \cite{MacKay:2002:Information_Theory_Learning,Turner:2011:Two_Problems_With_Variational_Expectation,Murphy:2012:Probabilistic_Perspective}. We further refine the MF approximation to alleviate these biases.

@@

% \subsection{RLC Series Circuit}
% Consider the voltage response $f(t)$ of a series circuit consisting of a resistance $R$, capacitance $C$, and inductance $L$ excited by current $x(t)$ with unity PSD due to thermal noise of the resistance. Application of Kirchhoff's voltage law \cite{Irwin:2010:Basic_Engineering_Circuit_Analysis} yields that
% \begin{align*}
%      L f'(t) + R f(t)+\frac{1}{C}\int^t f(t)\id{t} = x(t).
% \end{align*}
% Assume that the circuit is critically damped and that $R=2$ and $L=1$. Then $f(t)$ is of the form of \cref{eq:model} where $h(t) = t \exp(-t)$. Therefore, according to \cref{mod:cgpcm2}, it holds that $f(t) \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ where
% \begin{align*}
%     k_{f\cond h}(r) = \frac{1}{4}(1+|r|)\exp(-|r|).
% \end{align*}

% {\color{red} Experiment.}

% \subsection{Unvoiced Fricatives}
% Unvoiced fricatives are consonants produced by forcing air through a narrow constriction in the vocal tract, thereby creating a noisy, turbulant sound \cite{Taylor:2009:Text-To-Speech_Synthesis}.

\subsection{Speech}

@@

@@

\subsection{Population Growth}

@@

In future research on the CGPCM, various directions can be explored: First, the model could be extented to multidimensional input and output spaces by following a construction similar to that by \citet{Bruinsma:2016:GGPCM}. Second, the application of more efficient sparse approximation for $h$ and $x$, such as the tree-structured approximation \cite{Bui:2014:Tree-Structured_Gaussian}, would scale the CGPCM to larger data sets. Third, to deal with signals that are band-limited, but not necessarily baseband, the use of an harmonic interdomain transformation \cite{Tobar:2015:Inter-Domain_Inducing} could be explored.
%??? Fourth, in the low noise case, ESS has a hard time exploring $q(u)$; therefore, in that case, afternative sampling algorithms such as Hamiltonian Monte-Carlo \cite{Neal:2012:MCMC_Using_Hamiltonian_Dynamics} could be used.
Finally, using an approach similar to that by \citet{Lazaro-Gredilla:2013:Variational_Inference_for_Mahalanobis_Distance}, Bayesian inference in the hyperparameters could be attempted.
